---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MLR)
```

This package allows you to get some Important values in the multiple linear
Regression model.
\
\
There are two main functions and many small functions. They're closely related
to each other.
\
\
About the data set: we use build-in data test our data. Here we show the example
of `mtcars` data. In the test cases, `iris` data is also used to test our 
function.

## I. Function 

### 1.Summary Table coefficient values

R has its built-in function to generate this:
```{r}
linear_regression = lm(hp~mpg+wt,data = mtcars)
tab = summary(linear_regression)
tab
```

We can use our packages to generate these values. For example, for the 
coefficient part:
```{r}
X = unname(model.matrix(hp~mpg+wt,data = mtcars))
y = mtcars$hp
get_coef_table(X,y)
```

The value is exactly the same.


### 2.ANOVA

And we can generate an ANOVA table:
```{r}
get_anova(X,y)
```
We can compare it to ANOVA table that build-in function generates:
```{r}
anova(linear_regression)
```
The value is exactly the same.

### 3. Small Functions

Recall the output of the summary table:
```{r}
tab
```


This package can also generate the values of Multiple R-squared, 
Adjusted R-squared, Residual standard error and F-statistic. 
\
(Note: degrees of freedom of Residual 
standard error is the same as F-statistic df)
```{r}
sqrt(get_MSE(X,y))
get_Rsquare(X,y)
get_Radj(X,y)
get_F(X,y)
```


## II. Correctness

Here we test 2 functions: get_coef_table and get_anova
```{r}
ano_table = anova(linear_regression)

all.equal(unname(tab$coefficients),get_coef_table(X,y))
all.equal(unname(as.matrix(ano_table)),get_anova(X,y))

```


## III. Efficiency
Here we also test 2 functions: get_coef_table and get_anova.
\
\
For simplicity, we don't show the expression name here.

```{r}
bench::mark(unname(summary(lm(hp~mpg+wt,data = mtcars))$coefficients),
    get_coef_table(unname(model.matrix(hp~mpg+wt,data = mtcars)),mtcars$hp))[,-1]


bench::mark(unname(as.matrix(anova(lm(hp~mpg+wt,data = mtcars)))),
    get_anova(unname(model.matrix(hp~mpg+wt,data = mtcars)),mtcars$hp))[,-1]
```

We can find that the first function I build generating values for coefficient
summary table is slightly faster than the build-in function.
\
\
Surprisingly, the second function I build generating anova table values is
significantly faster than the build-in function.





