---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MLR)
```

This package allows you to get some Important values in the multiple linear
Regression model.

## Function 

### 1.Summary Table coefficient values

R has its built-in function to generate this:
```{r}
linear_regression = lm(hp~mpg+wt,data = mtcars)
tab = summary(linear_regression)
tab
```

We can use our packages to generate these values. For example, for the 
coefficient part:
```{r}
X = unname(model.matrix(hp~mpg+wt,data = mtcars))
y = mtcars$hp
get_coef_table(X,y)
```

The value is exactly the same.


### 2.ANOVA

And we can generate an ANOVA table:
```{r}
get_anova(X,y)
```
We can compare it to ANOVA table that build-in function generates:
```{r}
anova(linear_regression)
```
The value is exactly the same.


